---
title: "HW 5"
output: github_document
---

```{r, include = FALSE, messsage=FALSE, warning=FALSE}
library(tidyverse)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))


options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d


set.seed(1) #sets a seed for reproducibility
```

## Problem 2

Load data 

```{r, echo = FALSE, warning = FALSE, message = FALSE}
homicide_rawdf = read_csv("./data/homicide-data.csv")
```
This dataset overviews demographic and geographic data for homicide victims across various cities in the United States. 

```{r}
homicide_cleandf = 
  homicide_rawdf %>% 
  mutate(
    city_state = str_c(city,", ", state)
  )
```


```{r}
all_homicides = 
  homicide_cleandf %>% 
  group_by(city_state) %>% 
  summarize(n_obs = n())
```
```{r}
unsolved_homicides = 
  homicide_cleandf %>% 
  group_by(city_state) %>% 
  filter(
    disposition != "Closed by arrest"
  ) %>% 
  summarize(
    n_obs_unsolved = n()
  )
```

```{r}
homicide_city_state_data = 
  left_join(all_homicides, unsolved_homicides, by = "city_state")
```
```{r}

prop.test(5, 10) %>% 
  broom::tidy() %>% 
  select(
    estimate, conf.low, conf.high
  )

```

```{r}
sample = rnorm(30, mean = 0)

test_results = t.test(sample) %>% 
  broom::tidy()
```
```{r}
sim_t_test = function(true_mean) {
  sample = rnorm(30, mean = 0)
  
  test_results = t.test(sample) %>% 
  broom::tidy()
}

expand_grid(
  true_mean = 0:6, 
  iter = 1:5
)
```

Above, diff sample/diff sample mean but consistent true mean which is the input

Once you have the plot, it's all after you run the simulation 
group_by + summarize for the true mean & summarize how often the null was rejected

group_by averages 

If all you see are results where p< 0.5 --> publication bias; + low power 
 You end up seeing results which are different than true 
